Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-05-24 manuscript/manuscript.tex
Minor changes on Implementation
Modifications in Example with real data

It is based on the pre-existing code developed by \citet{Uieda2016} (and 
included in Fatiando a Terra v.0.5, \citet{Uieda2013}) that computes 
the gravitational effects of tesseroids with homogeneous density.
Our implementation keeps the the homogeneous tesseroid calculation and 
the modified adaptive discretization algorithm while incorporates the 
new variable density computations with the density-based discretization 
algorithm.
On their implementation, \citet{Uieda2016} have optimised the more time 
consuming functions through the Numba compiler.
In contrast, we have decided to develop our new library in Cython 
language due to difficulties when passing a Python function as argument 
to precompiled Numba methods.

@@

Besides all the tests we have carried out on the new code, we intend to show a 
forward modelling example with real data.

Besides the determination of the distance-size and the delta ratio, we 
wanted to show how the algorithm performs under a real data forward model.
In order to do it we have chosen the Neuqu\'en Basin: a sedimentary basin 
located to the east of the Andes, between 32$^\circ$S and 40$^\circ$S latitude 
(see Figure \ref{fig:neuquen-basin}a), that includes continental and marine 
siliciclastics, carbonates and evaporites accumulated over the Jurassic and 
the Cretaceous constituting a stratigraphic record up to 5000m of depth 
\citep{Howell2005}.

@@

The thickness of the sediment pack was obtained from \citet{Heine2007}.
We managed to produce a regular grid with a resolution of 0.05$^\circ$ on both 
longitude and latitude directions with one value of thickness on each node 
(see Figure \ref{fig:neuquen-basin}(b).

@@

We must also define a density function for the entire model.
\citet{Sigismondi2012} proposed a minimum and maximum density contrast for the 
Neuqu\'en basin of -412kg/m$^3$ and -275kg/m$^3$, respectively.
So we have chosen, for this specific example, an exponential density (like the 
one in equation \ref{eq:density-exp}) that assumes the minimum value on the 
surface and the maximum at 5858m, i.e. the bottom of the basin, with a value 
of $b$ equal to 2km.
This density function can be seen on Figure \ref{fig:neuquen-basin}(c).

>>>>

It is based on the pre-existing code developed by \citet{Uieda2016} (and 
included in Fatiando a Terra v.0.5, \citet{Uieda2013}) that computes 
the gravitational effects of tesseroids with homogeneous density.
Our implementation keeps the the homogeneous tesseroid calculation and 
the modified adaptive discretization algorithm while incorporates the 
new variable density computations with the density-based discretization 
algorithm.
On their software, \citet{Uieda2016} have optimised the more time 
consuming functions through the Numba compiler.
In contrast, we have decided to develop our new library in Cython 
language due to difficulties when passing a Python function as argument 
to precompiled Numba methods.

@@

Besides the determination of the distance-size and the delta ratio, we 
wanted to illustrate how the algorithm performs under a real data model.
For this task we have chosen the Neuqu\'en Basin: a sedimentary basin 
located to the east of the Andes, between 32$^\circ$S and 40$^\circ$S latitude 
(see Figure \ref{fig:neuquen-basin}a), that includes continental and marine 
siliciclastics, carbonates and evaporites accumulated over the Jurassic and 
the Cretaceous constituting a stratigraphic record up to 5000m of depth 
\citep{Howell2005}.

@@

The thickness of the sediment pack was obtained from \citet{Heine2007}.
We managed to produce a regular grid with a resolution of 0.05$^\circ$ on both 
longitude and latitude directions with one value of thickness on each node 
(see Figure \ref{fig:neuquen-basin}(b)).

@@

We must also define a density function for the entire model. 
\citet{Sigismondi2012} measured a minimum and maximum density contrast for 
the Neuqu\'en basin of -412kg/m$^3$ and -275kg/m$^3$, respectively.
So we have chosen, for this specific example, an exponential density (like the 
one in equation \ref{eq:density-exp}) that assumes the minimum value on the 
surface and the maximum at 5858m, i.e. the bottom of the basin, with a value 
of $b$ equal to 2km.
This density function can be seen on Figure \ref{fig:neuquen-basin}(c).
